---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
install.packages(c("dplyr", "tibble"))
```

# assignment1

<!-- badges: start -->
<!-- badges: end -->

The goal of assignment1 is to make accessible, clean, and tidy dataset for Assignment 1 of the course CGSC 5901/4900 X Special Topics in Cognitive Science: Advanced Statistics for Cognitive Science at Carleton University.

## Installation

You can install the development version of assignment1 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("romeopenheiro/assignment-1")
```

## Usage

The dataset is a tibble with 12,240 rows and 11 variables. A description of the variables is provided below.

```{r }
library(assignment1)
tibble::glimpse(DATASET)
```

Here is a sample of the rows.

```{r }
dplyr::slice_sample(DATASET)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

## Example

An example of the usage of the package can be seen by following this [link](https://github.com/romeopenheiro/CGSC5901/tree/main/assignment_1). 

