---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
install.packages(c("dplyr", "tibble"))
```

# assignment1

<!-- badges: start -->
<!-- badges: end -->

The goal of assignment1 is to make accessible, clean, and tidy dataset for Assignment 1 of the course CGSC 5901/4900 X Special Topics in Cognitive Science: Advanced Statistics for Cognitive Science at Carleton University.

## Installation

You can install the development version of assignment1 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("romeopenheiro/assignment-1")
```
## Data
Everything related to the dataset generated can be found in the following directory structure 

```bash
├── DESCRIPTION
├── LICENSE
├── LICENSE.md
├── NAMESPACE
├── R
│   ├── DATASET.R
│   ├── assignment1-package.R
│   └── utils-pipe.R
├── README.Rmd
├── README.md
├── assignment1.Rproj
├── data
│   └── DATASET.rda
├── data-raw
├── inst
│   └── rmarkdown
│       └── templates
│           └── assignment_template
│               ├── skeleton
│               │   └── skeleton.Rmd
│               └── template.yaml
└── man
    ├── DATASET.Rd
    ├── assignment1-package.Rd
    └── pipe.Rd
```

## Usage

The dataset is a tibble with 12,240 rows and 11 variables. A glimpse of the variables is provided below.

```{r }
library(assignment1)
tibble::glimpse(DATASET)
```

Here is a random sample of 6 rows.

```{r }
dplyr::slice_sample(DATASET, n = 6)
```

## Example

An example of the usage of the package can be seen by following this [link](https://github.com/romeopenheiro/CGSC5901/tree/main/assignment_1). 



## License

This project is licensed under the MIT License - see the [LICENSE.md](https://github.com/romeopenheiro/assignment-1/blob/main/LICENSE.md) file for details.
